Adopting agile in the large: motivations, success factors and challenges

### 2014-05-09 journal/article.tex
Using old and new models side by side: Work in progress

The difficulty of agile and misunderstandings were also evident in cases where
the methods were customized badly. As by-the-book implementation often was not
feasible the agile method was tailored to suit the needs of the organization.
However, in some cases tailoring meant skipping some practices, which lead into
problems. In one case certain individuals were allowed to ignore some core
elements of Scrum, which came to turn the teams decision making into a variant
of command and control [P9].
Lewis and Neher [P29] describe how there was temptation to strip some practices
and enhance others. Previous attempts had proven that one of the reasons early
attempts of agile had failed was deviations from the process, because of which
the agile mindset did not take root [P29]. In a bad implementation customization
may lead to the team taking only practices that reflect their current needs, and
therefore failing to achieve a real change in process and mindset [P9, P46].
Another example of bad customization that counteracts change is replacing agile
vocabulary by favoring familiar terminology from the old model [P44].

@@

@@

WORKING IN SILOS --> Certain expertise is required in many places

* Teams were reorganized without notice --> Planning was hampered when people did not konw who would stay on a team
* Frequent changes --> People managers had to agree to minimize team changes
[P11]
When we launched multiple Scrum teams, we tried to keep existing teams together
and form new teams based on skills.  As we gained experience, we realized that
there were skills shortages in certain types of expertise that wasn’t possible
to develop in a sprint or two. There was pressure to move engineers with certain
skills to the teams that needed them for work on upcoming sprints or to address
critical customer requirements.  When moves occurred without much notice, teams
couldn’t plan effectively if they didn’t know who would stay on a team.  After
several months of frequent changes, product owners and people managers agreed to
minimize team changes, and even talked of instituting a “trading deadline.”

>>>>

The difficulty of agile and misunderstandings were also evident in cases where
the methods were customized badly. As by-the-book implementation often was not
feasible the agile method was tailored to suit the needs of the organization.
However, in some cases tailoring meant skipping some practices, which lead into
problems. In one case certain individuals were allowed to ignore some core
elements of Scrum, which came to turn the teams decision making into a variant
of command and control [P9].
Lewis and Neher [P29] describe how there was temptation to strip some practices
and enhance others. Previous attempts had proven that one of the reasons early
attempts of agile had failed was deviations from the process, because of which
the agile mindset did not take root [P29]. In a bad implementation customization
may lead to the team taking only practices that reflect their current needs, and
therefore failing to achieve a real change in process and mindset [P9, P46].
Another example of bad customization that counteracts change is replacing agile
vocabulary in favor of familiar terminology from the old model, because
introducing new language will also create new ways of thinking [P44].

@@

In most cases a large organizational transformation proceeded gradually, and
during the process it was possible that the new agile model was used in parallel
with the old methods.

Ongoing projects were set up with previous development methods, and the agile
methods had to be arranged to fit with them [P8, P29].

Using the old and new models side by side was seen as problematic [P26], and
causing tensions on all organizational levels [P10].

As Scrum teams did not commit to fixed schedules teams working according to the
original model labeled them unreliable [P45].

The agile teams were required to comply with current procedures producing excess
documentation and stepping through approval gates [P20, P21]. The bureucracy of
the previous traditional model was still enforced, and management was not
convinced to lighten the process. In one case it was described that after
introducing the agile method teams were required to fill in templates of two
processes [P48].

Despite the agile introduction development was attempted to be managed in the
old waterfall fashion. O'Connor [P38] described management as ``focused on
meetings and big up front project plans''. In another case management was losing
confidence in agile because familiar reports on cost analysis and percentage
complete were not produced [P35].

A particular problem in sychronizing work between projects using different
models was that in Scrum the software design was fleshed out over time as
sprints progressed, but the waterfall model would require detailed design to be
locked early in the project [P29].

@@
